A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-17 src/paper.tex
Finished text corrections and added Lucas as author

\author{\IEEEauthorblockN{Ricardo E. V. de S. Rosa}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\ Federal University of Minas Gerais \\ Av. Antônio Carlos 6627, 31270-901, \\Belo Horizonte, MG, Brazil\\
Email: ricardoerikson@ufmg.br}
\and
\IEEEauthorblockN{Vicente F. de Lucena Junior}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\
Federal University of Amazonas \\
Manaus, AM, Brazil\\
Email: vicente@ufam.edu.br}
}
\maketitle

@@

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume.

@@

Initially, the CP infrastructure must provide an authentication mechanism so that viewers and their interactive TV (iTV) devices (e.g., set-top boxes or smart TVs) can be authenticated by the CP in order to use the secondary screen services. Once one iTV device is authenticated, the viewers in the TV environment must link their user accounts with the iTV device. As a result, the viewer can use their personal device as a secondary screen for that iTV device, enabling the capture of viewers' interactions.

The architecture to accurately capture viewers interactions is shown in Figure~\ref{fig_architecture}. This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) an iTV device, and the CP infrastructure (which includes an application hosting infrastructure). The green arrows represent the data flowing from the viewer to the CP infrastructure, while blue arrows denote the flow from CP infrastructure to the viewers. The black arrows represent the data flow inside the CP infrastructure.

@@

The STB has a presence service which detects nearby devices with viewer accounts linked to the STB. Once the STB and a linked secondary screen device are in the same environment, they are synchronized in order to update contextual data about viewer profile and amount of people using a secondary device in the room. This contextual information can be used to learn how a viewer behave toward other viewers. For example, a viewer behaves in a particular way while watching TV alone and the same viewer can behave in a different way while watching in group.

Viewers can use their secondary screen device to interact with TV by evaluating, commenting, sharing or even recommending TV content to other viewers. These interactions and the contextual information are represented by the audience data that is then sent to CP infrastructure through Internet. Then, a Data Writer service stores the audience data related to each individual viewer and STB device that are authenticated in the TV environment.

@@

Since applications in the TV domain have the potential to reach out to millions of users at the same time, it is interesting that the CP infrastructure has the ability to deal with a large amount of incoming data~\cite{Lee2010}. The captured data is individual and when it is associated with the context it can provide valuable information about viewers. By using proper machine learning algorithms this data can provide valuable information about viewers. Knowing this information can be very useful for CPs to improve their services aiming to increase the audience and enrich user experience. As an example, CPs can deliver personalized content for a single person as well as for groups of people by using content recommendation algorithms.

The use of personal devices as secondary screens arises as a new trend in TV environments. The architecture described in this paper take advantage of the ubiquity and computational capabilities of secondary screen devices to identify viewers and provide feedback for CPs through viewers' interactions and contextual information.

>>>>

\author{\IEEEauthorblockN{Ricardo E. V. de S. Rosa}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\ Federal University of Minas Gerais \\ Av. Antônio Carlos 6627, 31270-901, \\Belo Horizonte, MG, Brazil\\
Email: ricardoerikson@ufmg.br}
\and
\IEEEauthorblockN{Lucas C. Cordeiro and Vicente F. de Lucena Junior}
\IEEEauthorblockA{Graduate Program in Electrical Engineering \\
Federal University of Amazonas \\
Manaus, AM, Brazil\\
Email: vicente@ufam.edu.br}
}
\maketitle

@@

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume.

@@

Initially, the CP infrastructure must provide an authentication mechanism so that viewers and their interactive TV (iTV) devices (e.g., set-top boxes or smart TVs) can be authenticated by the CP in order to use the secondary screen services. Once one iTV device is authenticated, the viewers in the TV environment must link their user accounts up with the iTV device. As a result, the viewer can use their personal device as a secondary screen for that iTV device, enabling the capture of viewers' interactions.

The architecture to accurately capture viewers interactions is shown in \figurename~\ref{fig_architecture}. This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) an iTV device, and the CP infrastructure (which includes an application hosting infrastructure). The green arrows represent the data flowing from the viewer to the CP infrastructure, while blue arrows denote the flow from CP infrastructure to the viewers. The black arrows represent the data flow inside the CP infrastructure.

@@

A presence service detects nearby secondary screen devices that have the services necessary for establishing a communication with iTV device. Once the secondary screen device is linked up with the iTV device in the same environment, they are synchronized in order to update contextual data about viewer profile and amount of people using a secondary device in the room. This contextual information can be used to learn how a viewer behave toward other viewers. For example, a viewer behaves in a particular way while watching TV alone and the same viewer can behave in a different way while watching in group.

Viewers can use their secondary screen device to interact with TV by evaluating, commenting, sharing or even recommending TV content to other viewers. These interactions and the contextual information are represented by the audience data that is then sent to CP infrastructure through Internet. Then, a Data Writer service stores the audience data related to each particular viewer and the iTV device.

@@

Since applications in the TV domain have the potential to reach out to millions of users at the same time, it is interesting that the CP infrastructure has the ability to deal with a large amount of incoming data~\cite{Lee2010}. The captured data relates to a single viewer in a given context. By using proper machine learning algorithms this data can provide valuable information about viewers. Knowing this information can be very useful for CPs to improve their services aiming to increase the audience and enrich user experience. As an example, CPs can deliver personalized content for a single person as well as for groups of people by using content recommendation algorithms.

The use of personal devices as secondary screens arises as a new trend in TV environments. The architecture described in this paper take advantage of the ubiquity and interactive capabilities of secondary screen devices to identify viewers and provide feedback for CPs through viewers' interactions and contextual information.
